Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-28 TACAS2018/paper.tex
nudge

\item Select a sample time ($T_d$) that minimizes the magnitudes of the matrices used in both the
implementation and the abstraction. This ensures that a small word length for the plant precision is required for

@@

If we cannot optimize the candidate  we signal the {\sc Abstract} phase to potentially 
increase the precision and 
%phase to
%refine $\phi$ and
request {\sc Synthesise} to produce a new
candidate.  Otherwise the optimized candidate solution is given back to
{\sc Verify Synthesis}.
\note{when is the precision increased in abstract?}

@@

CEGIS-OR shows promise in exploiting modularity for improved response. 
It however relies on the use of application-specific optimization, 
which requires adequate tools for exploring different types of properties.  
Our results show significant improvement in terms of scalability over standard CEGIS approaches, 
with an ability to explore complex properties, hence many synthesis tasks may be tackled with it. 
In particular we note that our synthesis loop should be targeted at 
models where the solution space is formed by connected spaces where
optimization algorithms or localized synthesis are likely to be achieved more
efficiently than global synthesis \note{such solution spaces are unlikely classifiable a priori}. 
Finally our application to control synthesis provides a solid proof
of concept for scalable optimal control synthesis of LTI systems.

>>>>

\item Select a sample time ($T_d$) that minimizes the magnitudes of the used matrices.
This ensures that a small word length for the plant precision is required for

@@

If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
use the updated $\phi_\mathit{synth}$ and request {\sc Synthesise} to produce a new
candidate.  Otherwise the optimized candidate solution is given back to
{\sc Verify Synthesis}.

@@

CEGIS-OR shows promise in exploiting modularity for improved response. 
It however relies on the use of application-specific optimization, 
which requires adequate tools for exploring different types of properties.  
Our results show significant improvement in terms of scalability over standard CEGIS approaches, 
with an ability to explore complex properties, hence many synthesis tasks may be tackled with it. 
In particular we note that our synthesis loop should be targeted at 
models where the solution space is formed by connected spaces where
optimization algorithms or localized synthesis are likely to be more
efficiently than global synthesis \note{such solution spaces are unlikely classifiable a priori}. 
Finally our application to control synthesis provides a solid proof
of concept for scalable optimal control synthesis of LTI systems.
